Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-15 content/appendix.tex
todo comment
finished proof of lemma 5

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] 
According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as
\begin{align*}\label{eq:transCcResultCc}
  \backCC(\resultIDE(\transCC_R(P)))(n)
  &=\{d'\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d'))(r)\ne\top_T\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\menv(q)(\Omega)(d')(r)\ne\top_T\right\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d'}(r)\ne\top_T\right\}.
\end{align*}
  According to~Lemma~\ref{lem:sound3}, since $d\in M_F(p)(\varnothing)$, then $\mpd(r)\ne\top_T$.
  Since $p\in\ivp(n)$,
  \begin{align*}
    \mpd(r)\subseteq\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)\,.
  \end{align*}
  From $\bigsqcap_{q\in\ivp(n)}\mpddef qd(r)=\rho(n,\,d)(r)$ it follows that
  $\mpd(r)\subseteq\rho(n,\,d)(r)$.
  Therefore, $\rho(n,\,d)(r)\ne\top_T$, and $d\in D_n^\Subset(\rho)=\backCC(\rho)(n)$.
\end{proof}

>>>>

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:sound}}] 
According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as
\begin{align*}\label{eq:transCcResultCc}
  \backCC(\resultIDE(\transCC_R(P)))(n)
  &=\{d'\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d'))(r)\ne\top_T\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\menv(q)(\Omega)(d')(r)\ne\top_T\right\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d'}(r)\ne\top_T\right\}.
\end{align*}
  According to~Lemma~\ref{lem:sound3}, since $d\in M_F(p)(\varnothing)$, then for any $r\in R$, $\mpd(r)\ne\top_T$. 
  Since $\mpd(r)$ is a non-empty set that is contained in $\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)$, it follows that $$\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)\ne\top_T.$$ Therefore, $d\in \backCC(\resultIDE(\transCC_R(P)))(n)$.
\end{proof}
